Iterative Monomorphisation

### 2024-03-21 iterative_monomorphisation.tex
more

The various bounds presented here overlap to some extent. For instance, limiting the number of substitutions generated at this step may be sufficient to curb the number of new type argument tuples, making the \textcolor{ourblueviolet}{\MonoCap}, \textcolor{ourblueviolet}{\MonoMult}, \textcolor{ourblueviolet}{\MonoFloor} triplet superfluous. Each bound nonetheless has its use cases. For example, problems that lead to few successful matches but many type arguments may benefit from a limit on the number of new type arguments whilst sets of problems where substitution generation is more explosive might consider a limit on the number of generated substitution to be more useful.

>>>>

The various bounds presented here overlap to some extent. For instance, limiting the number of substitutions generated at this step may be sufficient to curb the number of new type argument tuples, making the \textcolor{ourblueviolet}{\MonoCap}, \textcolor{ourblueviolet}{\MonoMult}, \textcolor{ourblueviolet}{\MonoFloor} triplet superfluous. Each bound nonetheless has its use cases. For example, problems that lead to few successful matches but many type arguments may benefit from a limit on the number of new type arguments whilst problems for which substitution generation is more explosive may benefit from a limit on the number of generated substitution.
